% ============================================================
%  ArcLoom Master Specification v5.0
%  Unified Architecture: Coherence-Field Lattice, TAL Physics,
%  BSIL Interop, WeaveSpec Programming, Physical Implementation
%  ISO-Grade Deterministic Specification
%  Overleaf-compatible LaTeX
% ============================================================
\documentclass[11pt, a4paper]{report}

\usepackage[margin=2.2cm]{geometry}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{booktabs, array, longtable, tabularx, multirow}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{caption}
\usepackage{float}
\usepackage{setspace}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!black,
  urlcolor=blue!60!black,
}

\definecolor{al-gold}{RGB}{180, 140, 60}
\definecolor{al-dark}{RGB}{30, 30, 30}
\definecolor{al-green}{RGB}{40, 120, 60}
\definecolor{al-red}{RGB}{160, 40, 40}
\definecolor{al-gray}{RGB}{100, 100, 100}
\definecolor{al-blue}{RGB}{40, 80, 160}

\pagestyle{fancy}
\fancyhf{}
\rhead{\textcolor{al-gray}{\small ArcLoom Master Specification v5.0}}
\lhead{\textcolor{al-gray}{\small Confidential --- Internal Use Only}}
\cfoot{\thepage}

\titleformat{\chapter}[display]{\bfseries\Huge}{Chapter \thechapter}{0.5em}{\Large}
\titleformat{\section}{\large\bfseries\color{al-dark}}{\thesection}{0.6em}{}
\titleformat{\subsection}{\normalsize\bfseries\color{al-dark}}{\thesubsection}{0.6em}{}
\titleformat{\subsubsection}{\normalsize\itshape\color{al-dark}}{\thesubsubsection}{0.6em}{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\onehalfspacing

\newtheorem{definition}{Definition}[chapter]
\newtheorem{axiom}{Axiom}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\newtheorem{requirement}{Requirement}[chapter]

\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

% ============================================================
\begin{document}

% ── Title Page ─────────────────────────────────────────────
\begin{titlepage}
\centering
{\Huge \textbf{ArcLoom}}\\[0.5cm]
{\LARGE Master Specification v5.0}\\[0.3cm]
{\Large Unified Architecture for Deterministic Structural Perception}\\[1cm]

\renewcommand{\arraystretch}{1.15}
\begin{tabularx}{\textwidth}{|p{0.28\textwidth}|Y|}
\hline
Document ID & ARC-MASTER-SPEC-5.0 \\\hline
Version & 5.0 --- Master Canon \\\hline
Status & Controlled specification \\\hline
Effective Date & 2026-04-10 \\\hline
Classification & Confidential --- Internal Use Only \\\hline
Author & Joseph Forrester \\\hline
Source Documents & ArcLoom Spec v0.3, v0.4, v1.0--v1.3; BSIL v0.1;
                   WeaveSpec v0.1; MathLoom v1.4; ArcLoom v4.0 \\\hline
Purpose & Consolidate all prior ArcLoom specifications into a single
          authoritative master document. Defines the complete architecture
          from coherence-field theory through physical implementation to
          reference platform design. \\\hline
Supersedes & All prior ArcLoom specifications. This document is the
             single source of truth. \\\hline
\end{tabularx}

\vfill
{\large \textbf{Non-Replacement Statement}}\\[0.2cm]
\parbox{0.93\textwidth}{ArcLoom is a structural perception processor.
It is not a general-purpose binary computer replacement. It excels at
detecting structural state transitions in continuous signals with bounded
latency, near-zero quiescent power, and deterministic safety guarantees.
For general-purpose computation (arithmetic, networking, storage), ArcLoom
coexists with conventional binary systems via the BSIL interoperability
layer.}
\vfill
\end{titlepage}

\tableofcontents
\clearpage

% ============================================================
% PART I: FOUNDATIONS
% ============================================================

\chapter{Introduction}

\section{What ArcLoom Is}

ArcLoom is a deterministic, non-von Neumann processor architecture for
\textbf{structural perception}. It does not execute instructions. It does
not interpret opcodes. It does not operate on a clock cycle.

Instead, ArcLoom:
\begin{enumerate}[nosep]
  \item Receives continuous sensor signals through \textbf{krimelack
        transduction rings}
  \item Injects structural evidence into a \textbf{coherence-field lattice}
        ($\psi$-lattice)
  \item Applies \textbf{Law-Fields} (constraint programs) and
        \textbf{Goals} (boundary terms) that shape the field's settling
        behavior
  \item Settles to equilibrium through \textbf{energy minimization} in a
        tri-stable attractor medium
  \item \textbf{Commits} history into folded structural memory
        (Krimelacks) when entropy collapses
  \item Emits bounded outputs through a minimal universal adapter
\end{enumerate}

The processor's ``computation'' is the physics of the field settling.
When the field reaches a structural lock, the output is not a calculation
--- it is a \textbf{geometric requirement} of the field.

\section{What ArcLoom Is Not}

\begin{itemize}[nosep]
  \item ArcLoom is \textbf{not} a general-purpose CPU replacement. It
        cannot run Excel, browse the web, or play video games.
  \item ArcLoom is \textbf{not} a neural network accelerator. It does not
        perform matrix multiplication or gradient descent.
  \item ArcLoom is \textbf{not} a quantum computer. It operates at room
        temperature on classical physics.
  \item ArcLoom \textbf{does not} use probability, statistics, or machine
        learning at any level.
\end{itemize}

For tasks requiring general-purpose computation, ArcLoom coexists with
binary systems through the \textbf{Binary Story Ingestion Layer (BSIL)}.

\section{Architecture Summary}

ArcLoom has five architectural layers:

\begin{center}
\begin{tabular}{@{}rll@{}}
\toprule
\textbf{\#} & \textbf{Layer} & \textbf{Function} \\
\midrule
1 & Coupler Array (Krimelacks) & Sensor transduction + output actuation \\
2 & Kernel Fabric (UF L0--L4) & Structural perception: gates, DSF, safety \\
3 & Loom Fabric ($\psi$-lattice + TAL) & Coherence-field evolution + attractor settling \\
4 & Memory Fabric (Krimelacks Memory) & Folded structural memory: motifs, strands, recall \\
5 & Governance \& Safety & SafeMode, hardening, bounded outputs \\
\bottomrule
\end{tabular}
\end{center}

Two additional specification layers define software and interoperability:
\begin{itemize}[nosep]
  \item \textbf{WeaveSpec:} Declarative programming surface (constraint
        bundles, not instructions)
  \item \textbf{BSIL:} Binary Story Ingestion Layer (coexistence with
        binary systems)
\end{itemize}

\section{Design Constraints (Diamond Hard)}

\begin{enumerate}[label=DC-\arabic*.]
  \item \textbf{Zero heuristics.} All thresholds derived from geometry
        or frozen rational constants.
  \item \textbf{Zero randomness.} No stochastic elements anywhere.
  \item \textbf{Zero ML.} No trained models, no gradient descent, no
        statistical inference.
  \item \textbf{Deterministic.} Identical inputs + parameters $\Rightarrow$
        identical outputs.
  \item \textbf{Domain agnostic.} The fabric computes structural state
        from any temporal signal.
  \item \textbf{Bounded.} All outputs, energies, and state variables have
        finite bounds.
  \item \textbf{Safe.} SafeMode is a mandatory architectural state, not
        an optional feature.
\end{enumerate}

% ============================================================
\chapter{Glossary of Terms}

\begin{longtable}{@{}p{4cm}p{10.5cm}@{}}
\toprule
\textbf{Term} & \textbf{Definition} \\
\midrule
\endhead
AIF & ArcLoom Invariant Fabric. The ternary computing substrate. \\
Arc & Mode overlap: the projection $A_i(k) = \langle \Phi_i, \psi(k) \rangle$.
     Arc weights $p_i = |A_i|^2 / \sum |A_j|^2$. \\
BSIL & Binary Story Ingestion Layer. Treats binary programs as story
       generators; captures observable behavior as structural episodes. \\
BCP & Binary Control Coprocessor. Conventional MCU supervisor in hybrid
      configuration. \\
Commit & The act of collapsing continuous lattice state into a discrete
         Fact Strand when entropy drops below threshold. \\
Coupling Matrix ($J_{ij}$) & Phase-coupling strengths between oscillator
                             rings. Derived from DSF-AI kernel structure. \\
DSF & Deterministic Structural Field. The 8-dimensional output vector of
      the UF L0--L4 kernel: $(D_k, M_k, R_{rev,k}, U^*_k, C_k, P_k, B_k, S_{UF})$. \\
Doorway Event & Local collapse of phase amplitude below $\epsilon$,
                indicating topological vulnerability (Negative Space). \\
Entropic Flip & The moment when lattice entropy $H_k$ drops and
                determinism index $Det_k$ rises above commit threshold. \\
Fact Strand & A committed structural episode stored in Krimelacks memory. \\
H1-C & Hardening Level 1 with Correction. Deterministic error recovery
       in hybrid mode. \\
Horizon Projection & Free evolution of $\psi$ with $J=0$ to project
                     future structural states. Structural imagination. \\
Krimelack & Dual function: (1) sensory transduction ring (I/O boundary),
            (2) folded structural memory (motif storage and recall). \\
Law-Field & Hermitian constraint operator applied to the $\psi$-lattice.
            ``Programs are constraint fields.'' \\
MapInject & Canonical mapping from UF evidence to $\psi$-lattice injection. \\
Mode Bank ($\Phi_i$) & Library of committed structural templates. Modes
                       grow from committed histories via centroid synthesis. \\
Motif & A structural pattern extracted from Fact Strands and stored in
        Krimelacks memory with adjacency weights. \\
Negative Space & Quiescent region where $\sigma < \sigma_{min}$,
                 $\|\Delta F\| < \delta_{min}$, $\kappa < \kappa_{min}$.
                 An active potential well, not a passive absence. \\
Parity Chain & Group of trits whose winding numbers must sum to a
               topological constant $K$. Geometric error correction. \\
SafeMode & Mandatory safety state: $J=0$, $H_{goal}=0$, commit frozen,
           memory frozen, outputs hold. \\
SL-1 & Structural Lock Level 1. L6-TCL output certifying geometric
       inevitability. \\
TAL & Ternary Attractor Loom. Physical compute primitive using
      tri-stable attractor cells. \\
Topological Schmitt Trigger & Nonlinear coupling term that forces
                              metastability resolution. \\
Trit & Ternary digit: $t \in \{-1, 0, +1\}$. \\
TSAC & Tri-Stable Attractor Cell. Physical element with three stable
       energy basins. \\
Weave & Declarative program bundle: couplers, laws, goals, memory
        policy, commit policy. Mounted, not executed. \\
Winding Number ($w$) & Integer topological invariant of a phase field
                       around a ring. Encodes trit state. \\
$\psi$-lattice & Coherence-field lattice. $\psi_n = \sqrt{\rho_n} e^{i\phi_n}$
                 evolving under Hermitian Hamiltonian. \\
\bottomrule
\end{longtable}

% ============================================================
\chapter{Mathematical Foundations}

\section{Notation}

\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
$\psi \in \mathbb{C}^N$ & Coherence-field lattice state \\
$\psi_n = \sqrt{\rho_n} e^{i\phi_n}$ & Amplitude-phase decomposition at node $n$ \\
$H$ & Hermitian Hamiltonian operator \\
$J(k)$ & Injection field at structural time $k$ \\
$\Phi_i$ & Mode template $i$ in the mode bank \\
$A_i(k) = \langle \Phi_i, \psi(k) \rangle$ & Arc: mode overlap \\
$p_i(k) = |A_i|^2 / \sum |A_j|^2$ & Arc weight (normalized) \\
$H_k = -\sum_i p_i \log p_i$ & Structural entropy \\
$Det_k = 1 - H_k/H_0$ & Determinism index \\
$w$ & Winding number (trit state) \\
$J_{ij}$ & Coupling matrix element \\
$\mathcal{L}_k$ & Law-Field set active at gate $k$ \\
$\mathcal{G}_k$ & Goal/boundary set active at gate $k$ \\
$E_{sys}$ & Total system energy \\
$V(x)$ & Tri-well potential function \\
\bottomrule
\end{tabular}
\end{center}

\section{Balanced Ternary Arithmetic}

The fundamental digit: $t \in \{-1, 0, +1\}$.

An $n$-trit word: $\text{val}(T) = \sum_{i=0}^{n-1} t_i \cdot 3^i$.

Properties: $\log_2 3 \approx 1.585$ bits/trit; symmetric signed
representation; negation by sign flip $\overline{t_i} = -t_i$; native
zero state represents quiescence.

\section{Winding Number}

\begin{definition}[Winding Number]
Continuous: $w = \frac{1}{2\pi} \oint \frac{d\phi}{d\theta}\, d\theta \in \mathbb{Z}$.

Discrete ($N$ samples): $w = \frac{1}{2\pi} \sum_{i=0}^{N-1} \text{wrap}(\phi_{i+1} - \phi_i)$,
$\phi_N \equiv \phi_0$.
\end{definition}

\section{Coherence-Field Evolution}

\begin{axiom}[$\psi$-Lattice Evolution]
The coherence field evolves under:
\begin{equation}
  \boxed{i\hbar \frac{d\psi}{d\tau} =
    \underbrace{[H_{base} + H_{mem} + H_{law}(\mathcal{L}_k) + H_{goal}(\mathcal{G}_k) + H_{safety}]}_{H_{total}(k)}
    \psi + J(k)}
\end{equation}
\end{axiom}

\textbf{Constraints:}
\begin{itemize}[nosep]
  \item $H_{total}(k)$ \textbf{must} be Hermitian (preserves norm)
  \item All interaction terms \textbf{must} be symmetric
  \item Integration method: Crank--Nicolson (norm-preserving, stable)
  \item Norm invariant: $| \|\psi\|^2(k) - \|\psi\|^2(k-1) | \leq \epsilon_{norm}$
\end{itemize}

\section{Tri-Stable Attractor Cell (TSAC)}

\begin{definition}[TSAC Energy]
A TSAC has three stable basins at $x \in \{-1, 0, +1\}$:
\begin{equation}
  V(x) = a x^6 - b x^4 + c x^2
\end{equation}
with $a, b, c$ chosen to create three distinct minima. Constants are
frozen rationals.
\end{definition}

\begin{definition}[TAL Energy Functional]
For a coupled array of TSACs:
\begin{equation}
  E(\mathbf{x}; \mathbf{b}, W) = \sum_i V(x_i) - \sum_{i<j} W_{ij} x_i x_j - \sum_i b_i x_i
\end{equation}
with $W$ symmetric. The system settles by damped gradient flow toward
energy minimum.
\end{definition}

\section{Nonlinear Coupling (Topological Schmitt Trigger)}

\begin{equation}
  E_{sys} = -\sum_{i,j} J_{ij} \left[ \cos(\Delta\phi_{ij})
            + \alpha \cos^3(\Delta\phi_{ij}) \right]
\end{equation}

$\alpha$ is a frozen rational constant. The cubic term deepens wells at
valid states and raises barriers at saddle points, forcing metastability
resolution within:
\begin{equation}
  t_{resolve} < \frac{1}{J \cdot \alpha \cdot \omega_0}
\end{equation}

\section{Capture Threshold and Structural Lock}

(From L6-TCL Specification.)

\begin{equation}
  \tau = 1 - \frac{\Gamma\!\left(\frac{n_{start}}{2}+1\right)}
                  {\Gamma\!\left(\frac{n_{eff}}{2}+1\right)}
  \cdot \pi^{(n_{eff}-n_{start})/2}
\end{equation}

Structural Lock fires when $n_{eff} < n_{start}/e$. Derived from
natural constants ($e$, $\Gamma$). Not a design parameter.

% ============================================================
\chapter{The $\psi$-Lattice Core}

\section{Description}

The $\psi$-lattice is the central evolving substrate of ArcLoom. It is a
coherence field --- a complex-valued vector $\psi \in \mathbb{C}^N$ where
each component $\psi_n = \sqrt{\rho_n} e^{i\phi_n}$ carries both amplitude
(structural weight) and phase (structural relationship).

The lattice evolves deterministically under a Hermitian Hamiltonian. It
does not ``compute'' in the von Neumann sense. It \textit{settles} ---
finding the energy minimum of the combined constraint field formed by
base coupling, memory influence, active laws, active goals, and safety
boundaries.

\section{Injection Mapping (MapInject)}

UF L0--L4 kernel outputs are mapped into injection fields that perturb
the $\psi$-lattice:

\textbf{Evidence packing:}
\begin{equation}
  e_k = \text{concat}\!\left( \text{norm}(TVR_k),\; ISF_k,\; URF_k,\; DSF_k,\; N(G_k) \right)
\end{equation}

\textbf{Injection amplitude:}
\begin{equation}
  a_k = \text{clamp}\!\left( a_0 \cdot w_k \cdot URF_k \cdot (1-U^*_k) \cdot (1-N(G_k)),\; [0, a_{max}] \right)
\end{equation}

\textbf{Injection field:}
\begin{equation}
  J(k) = a_k \cdot \text{normalize}(P_{in} \cdot e_k)
\end{equation}

where $P_{in}$ is a deterministic orthonormal projection matrix constructed
from a configuration seed (OD-4, locked: Option B).

Constraints: $\|J(k)\| \leq J_{max}$; SafeMode $\Rightarrow J(k) = 0$;
Negative Space $\Rightarrow a_k \leq a_{NS,max}$.

\section{Mode Overlaps, Entropy, and Commit}

\textbf{Arc computation:}
$A_i(k) = \langle \Phi_i, \psi(k) \rangle$, \quad
$p_i(k) = |A_i|^2 / \sum_j |A_j|^2$.

\textbf{Entropy and determinism:}
$H_k = -\sum_i p_i \log p_i$, \quad
$Det_k = 1 - H_k / H_0$.

\textbf{Commit condition (Entropic Flip):}
\begin{equation}
  \text{commit}(k) = 1 \iff Det_k \geq Det_{commit} \;\text{AND}\; \max_i p_i(k) \geq p_{commit}
\end{equation}

When commit fires, the current $\psi$ state is captured as a Fact Strand
and folded into Krimelacks memory. The dominant mode $\Phi_{i^*}$ receives
reinforcement.

\section{Horizon Projection (Structural Imagination)}

Free-evolve $\psi$ with zero injection to project future states:

\begin{equation}
  \hat{\psi}(k+h) = \text{FreeEvolve}\!\left( \hat{\psi}(k+h-1),\; H_{total}(\mathcal{L}_k, \mathcal{G}_k),\; J=0 \right)
\end{equation}

for $h = 1 \ldots H$. Compute projected arcs $\hat{p}_i(k+h)$ and
projected $\widehat{DSF}(k+h)$.

This is \textbf{structural imagination}: the system explores what the
field would do if left undisturbed. It enables anticipatory behavior
without prediction or probability.

Constraint: projection weight in output $\leq w_{proj,max}$ (bounded
influence).

% ============================================================
\chapter{Law-Fields: The Programming Model}

\section{Core Concept}

ArcLoom does not have instructions. It has \textbf{Law-Fields}: selectable
constraint sets applied as Hermitian operators that shape how the
$\psi$-lattice settles. ``Programs are constraint fields.''

\begin{equation}
  H_{law}(\mathcal{L}_k) = \sum_{j \in \mathcal{L}_k} \gamma_j L_j
\end{equation}

Every $L_j$ \textbf{must} be Hermitian ($L_j = L_j^\dagger$). Any potential
term must be bounded below.

\section{Canonical Law Families}

\begin{enumerate}[label=(\Alph*)]
  \item \textbf{Symmetry Law:} $L_{sym} = (I - T)^\dagger(I - T)$ for a
        unitary transform $T$. Penalizes asymmetry.
  \item \textbf{Consistency Law:} $L_{cons} = \sum_{(n,m)} a_{nm}(|n\rangle\langle n| - |m\rangle\langle m|)^2$
        weighted by motif adjacency. Penalizes inconsistency with memory.
  \item \textbf{Compactness Law:} $U_{comp}(\rho) = \lambda_{comp} \sum_n f(\rho_n)$
        with $f$ convex. Penalizes diffuse states.
\end{enumerate}

\section{Law Selection Policy}

When multiple law sets apply, selection uses \textbf{minimum action
increment} ($\Delta S_{total}$). This is intrinsic and deterministic ---
the law set that requires the least total structural change is preferred.

\section{Goal and Boundary Terms}

\begin{equation}
  H_{goal}(\mathcal{G}_k) = \sum_{g \in \mathcal{G}_k} \eta_g G_g
\end{equation}

Canonical goal: readout operator $O_{out}$ maps $\psi$ to output space.
$E_{goal} = \|O_{out}\psi - y_{target}\|^2$.

SafeMode $\Rightarrow H_{goal} = 0$. Bound: $\|H_{goal}\| \leq H_{goal,max}$.

% ============================================================
\chapter{Krimelacks: Sensory Transduction \& Structural Memory}

\section{Dual Role}

Krimelacks serve two architectural functions:
\begin{enumerate}[nosep]
  \item \textbf{Sensory transduction rings} --- the I/O boundary between
        environment and fabric
  \item \textbf{Folded structural memory} --- where committed Fact Strands
        are stored, organized, and recalled
\end{enumerate}

\section{Sensory Transduction}

A krimelack is an oscillator ring whose natural frequency is modulated by
an external physical signal:
\begin{equation}
  \omega_{krim}(t) = \omega_0 + \kappa \cdot s(t)
\end{equation}

Phase accumulation produces winding-number transitions at structural
thresholds:
\begin{equation}
  \Delta w = \left\lfloor \frac{1}{2\pi} \int_0^T [\omega_{krim}(t) - \omega_0]\, dt + \frac{1}{2} \right\rfloor
\end{equation}

No analog-to-digital conversion required. The environment and the
processor share a continuous physical coupling.

\subsection{Sensor Types}

\begin{center}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Sensor} & \textbf{Signal} & \textbf{Transduction} & \textbf{Type} \\
\midrule
Vision & Pixel intensity & Photoresistor $\to \omega$ & Optical \\
Depth & Distance & Capacitive $\to \omega$ & Range \\
Motion & Acceleration & Piezo $\to \omega$ & Inertial \\
Proximity & Object distance & Reflective $\to \omega$ & Proximity \\
Temperature & Thermal & Thermistor $\to \omega$ & Thermal \\
\bottomrule
\end{tabular}
\end{center}

\section{Folded Structural Memory}

Krimelacks memory stores committed Fact Strands as motifs with adjacency
weights and spatial locality.

\textbf{State:} $V$ motifs, $W_{adj}$ adjacency weights, $pos$ locality map.

\textbf{Reinforcement:}
$W_{adj}(u,v) \leftarrow W_{adj}(u,v) + \eta_{mem} \cdot \text{score}(u,v,\text{strand})$

\textbf{Decay (Forgetting):}
$W_{adj}(u,v) \leftarrow (1 - \lambda_{mem}) \cdot W_{adj}(u,v)$

Decay is the Negative Space operator applied to memory. Structure is not
deleted --- it is compressed into quiescence. Decayed motifs can re-ignite
if the right structural trigger appears. This is how a smell recalls
childhood.

\textbf{Merge:}
If $W_{adj}(u,v) \geq \tau_{merge}$, merge motifs deterministically.

\textbf{Locality Folding:}
\begin{equation}
  \text{Cost}(pos) = \sum_{u,v} W_{adj}(u,v) \cdot \text{dist}(pos(u), pos(v))
\end{equation}
Update $pos$ to reduce Cost within tolerance $\epsilon_{fold}$. Structurally
related motifs remain physically near each other for efficient recall.

% ============================================================
\chapter{Physical Geometry: The Triple-Node Resonant Ring}

\section{Trit Register}

A single trit consists of three nonlinear oscillators (Nodes $A$, $B$, $C$)
in equilateral arrangement, coupled via phase-shifting delay lines.

\begin{center}
\begin{tabular}{@{}clll@{}}
\toprule
$w$ & State & Phase Relationship & Meaning \\
\midrule
$0$  & Quiescent & $\phi_A = \phi_B = \phi_C$ & No flow \\
$+1$ & CW Flow   & $\phi_B = \phi_A + 2\pi/3$, $\phi_C = \phi_B + 2\pi/3$ & Clockwise \\
$-1$ & CCW Flow  & $\phi_C = \phi_A + 2\pi/3$, $\phi_B = \phi_C + 2\pi/3$ & Counter-clockwise \\
\bottomrule
\end{tabular}
\end{center}

Energy barrier between adjacent states:
$\Delta E = J \cdot (1 + 3\alpha/4) \cdot 1.5$.
For $J = 1$, $\alpha = 37/64$: $\Delta E \approx 2.37$.

\section{Coupling Matrix ($J_{ij}$): The Instruction Set}

The coupling matrix encodes the computational topology. It is derived
from the DSF-AI kernel structure:

\begin{center}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Kernel Output} & \textbf{Target} & \textbf{$J_{ij}$ Derivation} \\
\midrule
$D_k$ & Direction pair & $J = D_k \cdot J_{base}$ \\
$S_{UF}$ & Convergence pair & $J = S_{UF} \cdot J_{base}$ \\
$M_k$ & Momentum pair & $J = |M_k| \cdot J_{base}$ \\
$C_k$ & Binding pair & $J = C_k/(1+C_k) \cdot J_{base}$ \\
$P_k$ & Compression pair & $J = P_k/(1+P_k) \cdot J_{base}$ \\
$B_k$ & Conviction pair & $J = |B_k| \cdot J_{base}$ \\
$U^*_k$ & Freedom pair & $J = -(U^*_k) \cdot J_{base}$ \\
$R_{rev,k}$ & Path-kill pair & $J = R_{rev,k} \cdot J_{max}$ \\
\bottomrule
\end{tabular}
\end{center}

$J_{base}$ and $J_{max}$ are frozen rational constants.

\section{Geometric Error Correction: Parity Chains}

Groups of $P = 5$ trits with topological parity constant $K$:
$\sum_{i=1}^{P} w_i = K$.

Restoring force: $F_{restore,i} = -\lambda_{parity}(\sum_j w_j - K)$.

Single-trit error correction without binary logic.

% ============================================================
\chapter{Configuration A: Pure Ternary}

All computation, error correction, and I/O through topological phase
dynamics. No binary logic, no clock, no instruction set.

\textbf{Logic:} Resonance Junctions --- coupled rings settle to energy
minimum producing deterministic output.

\textbf{Error correction:} Parity chains + topological Schmitt trigger.

\textbf{Power:} $P_{avg} = N_{rings} \cdot \rho_{transition} \cdot E_{transition}$.
Near-zero during quiescence.

\textbf{Metastability:} Resolved within $t_{resolve} < 1/(J \cdot \alpha \cdot \omega_0)$.

\textbf{Output:} $v_{motor} = w_{out} \cdot v_{max}$ ($w \in \{-1, 0, +1\}$:
reverse, stop, forward).

% ============================================================
\chapter{Configuration B: Hybrid (AHPP)}

ArcLoom Invariant Fabric (AIF) supervised by Binary Control Coprocessor (BCP).

\textbf{BCP functions:} timing, H1-C error correction, binary fallback,
memory management, safety monitoring.

\textbf{Doorway detection:} $\delta_j^{ext} = 1$ if $\min(a_i) < \epsilon_{gate}$.

\textbf{H1-C policy:} STALL $\to$ amplitude heal $\to$ relaxation ($R$ cycles)
$\to$ verify winding $\to$ recovered / corrected / binary fallback.

\textbf{Binary fallback:} BCP maintains complete L0--L4 kernel in binary.
Substitutes binary output if AIF produces uncorrectable result.

% ============================================================
\chapter{WeaveSpec: The Programming Surface}

\section{Description}

A \textbf{Weave} is the ArcLoom equivalent of an application. It is a
declarative JSON bundle specifying:
\begin{itemize}[nosep]
  \item Couplers (input/output bindings to krimelacks)
  \item Laws (which Law-Fields to activate)
  \item Goals (boundary terms and targets)
  \item Memory policy (reinforcement/decay rates)
  \item Commit policy (thresholds)
  \item Governance (safety bounds)
\end{itemize}

\textbf{Weaves are mounted, not executed.} Mounting a Weave configures
the coupling matrix, activates law sets, and binds I/O. The physics does
the rest.

\section{Lifecycle}

\begin{center}
AUTHORED $\to$ VALIDATED $\to$ MOUNTED $\to$ RUNNING $\to$ COMMITTING $\to$ UNMOUNTED
\end{center}

\section{Determinism Guarantee}

No hidden randomness. Seeds are explicit. Tie-breaks are deterministic
(lowest index). Fixed numeric precision.

% ============================================================
\chapter{BSIL: Binary Story Ingestion Layer}

\section{Description}

BSIL enables ArcLoom to coexist with binary systems without contaminating
the ternary/topological core. It treats legacy programs as \textbf{story
generators} --- observing their behavior rather than interpreting their
instructions.

\section{Capture Mechanism}

BSIL observes:
\begin{itemize}[nosep]
  \item User inputs (keyboard, mouse, touch)
  \item API calls and responses
  \item File system operations
  \item Render output (screen state)
\end{itemize}

These observables are captured as time-indexed structural episodes and
injected into the $\psi$-lattice through MapInject. ArcLoom does not
\textit{run} the binary program --- it \textit{learns the shape} of the
workflow as committed motifs.

\section{Compatibility Modes}

\begin{center}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Mode} & \textbf{Function} & \textbf{Binary Required} \\
\midrule
Shadow & Observe only & Yes (binary runs) \\
Assist & Observe + suggest & Yes (binary runs, ArcLoom advises) \\
Replacement & Motif-driven weave & No (ArcLoom replays from memory) \\
\bottomrule
\end{tabular}
\end{center}

Replacement mode is the long-term goal: ArcLoom has observed enough
workflows that it can reproduce the structural behavior without the
binary system running.

% ============================================================
\chapter{L6-TCL Integration: The Dimensional Grinder}

The ArcLoom fabric physically instantiates the L6 Topological Constraint
Layer. As constraints from the kernel restrict the coupling matrix, the
fabric's effective dimensionality reduces:

\begin{equation}
  n_{eff} = n_{start} - \sum_{i=1}^{k} \text{rank}(C_i)
\end{equation}

When $n_{eff} < n_{start}/e$, the fabric enters the capture basin.
SL-1 manifests as a global phase lock (pure) or hardware interrupt (hybrid).

% ============================================================
\chapter{Governance, Safety, and Hardening}

\section{SafeMode}

When SafeMode is active:
\begin{itemize}[nosep]
  \item $J(k) = 0$ (no injection)
  \item $H_{goal} = 0$ (no goal pressure)
  \item $\text{commit}(k) = 0$ (no memory writes)
  \item Memory updates frozen
  \item Outputs hold to $Y_{hold}$ (neutral)
\end{itemize}

\section{Invariants}

\begin{enumerate}[nosep]
  \item $\|\psi\|^2$ conserved within $\epsilon_{norm}$
  \item All values finite (no NaN/INF)
  \item Commit rate $\leq$ commit\_max per window
  \item Output $\|y_k\| \leq Y_{max}$
  \item Stale outputs ($k - k_{emit} > TTL_g$) $\Rightarrow Y_{hold}$
\end{enumerate}

\section{Determinism Rules}

\begin{enumerate}[nosep]
  \item No hidden randomness
  \item Stable tie-breaks (lowest index)
  \item Fixed numeric precision and ordering
  \item Class A: IEEE-754 float64 (reference)
  \item Class B: fixed-point (hardware, quantization bounded)
\end{enumerate}

% ============================================================
\chapter{Familiarity Feedback: Clockless Habituation}

\section{Motivation}

A purely combinational SPPU with fixed coupling weights and a fixed dead
zone produces identical output for identical input. This is deterministic
and correct, but creates a failure mode: the system cannot escape repeated
situations (e.g.\ a robot trapped in a corner repeating the same action).

Traditional solutions (timers, counters, randomness) require a clock and
violate the clockless principle of the SPPU.

\section{The Biological Principle}

Nothing in nature has a clock. Biological systems escape repetition through
mechanisms that share one principle: \textbf{the act of responding to a
specific input depletes the system's ability to respond to that same input
again.}

\begin{itemize}[nosep]
  \item \textbf{Synaptic depletion:} Repeated firing exhausts neurotransmitter
        supply at the synapse. Signal weakens because the resource was consumed,
        not because time passed.
  \item \textbf{Receptor saturation:} Olfactory receptors fill with the same
        molecule and stop responding. Novel molecules use different receptors
        at full sensitivity.
  \item \textbf{Neural adaptation:} Photoreceptors change sensitivity based on
        sustained stimulation. The substrate itself alters its response.
  \item \textbf{Refractory period:} After firing, ion channels require physical
        recovery. The neuron cannot fire regardless of input strength.
\end{itemize}

The common thread: the medium itself remembers what it has been doing, and
doing the same thing exhausts the response. Not time. Not a counter.
Experiential depletion.

\section{Mechanism: Krimelack Recall as Dead-Zone Feedback}

Krimelack recall is combinational --- the loom state is compared against all
stored motifs in parallel and a match score appears on the output wire in
one propagation delay.

\textbf{The match score feeds back into the SPPU dead zone:}

\begin{equation}
  \Delta_{\text{eff}} = \Delta_{\text{base}} + \text{match\_score}
\end{equation}

Each \texttt{arcloom\_local\_field} instance receives the krimelack match score
as an additional input. The tri-state comparator uses $\Delta_{\text{eff}}$
instead of the fixed $\Delta_{\text{base}}$.

This creates a combinational feedback loop:

\begin{enumerate}[nosep]
  \item SPPU settles $\rightarrow$ 48-bit loom state
  \item Loom state $\rightarrow$ krimelack recall $\rightarrow$ match score
  \item Match score $\rightarrow$ raises dead zone in SPPU
  \item Raised dead zone $\rightarrow$ marginally committed trits drop to null
  \item Different loom state $\rightarrow$ different match score
  \item Loop finds equilibrium: the settlement \textbf{maximally unlike}
        anything in krimelack, consistent with coupling pressures
\end{enumerate}

No clock. No timer. No register in the feedback path. Purely combinational.

\section{Behavioral Consequences}

\begin{description}[nosep]
  \item[Novel input] (no matching motif): match score $\approx 0$, dead zone
    stays at base, full sensitivity, normal response.
  \item[First repetition] (one matching motif): match score moderate, dead zone
    rises to $\sim$30--35. Trits with coupling pressure in $[20, 35]$ drop to
    null. Different decision emerges.
  \item[Multiple similar experiences] (several similar motifs): match score high,
    dead zone rises to 40+. Only very strongly coupled trits commit. System
    forced into a maximally novel response.
  \item[New situation] (after leaving the repeated state): different loom state
    $\rightarrow$ low match score $\rightarrow$ dead zone returns to base
    $\rightarrow$ full sensitivity restored.
\end{description}

\section{Loop Stability}

The combinational loop either finds a stable fixed point (the most novel
response consistent with coupling pressures) or oscillates between two
states (visible hesitation --- correct behavior for genuine indecision).

If oscillation is unstable, feedback gain is reduced:

\begin{equation}
  \Delta_{\text{eff}} = \Delta_{\text{base}} + (\text{match\_score} \gg k)
\end{equation}

where $k = 1, 2, 3$ reduces feedback strength by factors of 2, 4, 8.
Optimal $k$ is determined experimentally.

\section{TSAC ASIC: Native Substrate Habituation}

On ferroelectric TSACs, habituation is a free physical property. Sustained
polarization causes \textbf{dielectric fatigue} --- the potential barrier
rises with sustained identical state:

\begin{itemize}[nosep]
  \item Trit at $+1$, coupling pressure 25, base barrier 20 $\rightarrow$ commits
  \item Sustained $+1$ $\rightarrow$ barrier rises: 20 $\rightarrow$ 22 $\rightarrow$ 25 $\rightarrow$ 28
  \item Barrier exceeds pressure (28 $>$ 25) $\rightarrow$ trit falls to null
  \item Null (rest) $\rightarrow$ barrier recovers $\rightarrow$ fresh sensitivity
\end{itemize}

The RC time constant of the ferroelectric material IS the habituation rate.
No circuit. No logic. Physics.

On ASIC, two habituation layers operate simultaneously:
\begin{itemize}[nosep]
  \item \textbf{Substrate} (TSAC fatigue): fast, local, per-trit depletion
  \item \textbf{Cognitive} (krimelack feedback): slower, global, pattern-level familiarity
\end{itemize}

\section{Cognitive Implications}

Familiarity feedback is not an engineering patch. It is a fundamental
property of any system that learns from experience:

\begin{itemize}[nosep]
  \item \textbf{Novelty seeking:} Familiar states are harder to commit to.
    The system naturally gravitates toward unfamiliar states. Curiosity as
    a physical property, not a reward signal.
  \item \textbf{Attention:} Novel stimuli receive full coupling sensitivity.
    Repeated stimuli receive diminished sensitivity. Attention emerges from
    dead-zone dynamics.
  \item \textbf{Boredom:} Sustained identical input raises the dead zone until
    no trits can commit. The system goes silent. Change the input and full
    sensitivity returns.
  \item \textbf{Creativity:} When familiar responses are suppressed, the only
    available decisions are ones the system has never produced before.
    Structured novelty constrained by coupling weights.
\end{itemize}

\section{Implementation Summary}

\begin{longtable}{@{}lll@{}}
\toprule
\textbf{File} & \textbf{Change} & \textbf{Type} \\
\midrule
\endhead
\texttt{arcloom\_local\_field} & Add \texttt{dead\_zone\_adj} input (8-bit) & Combinational \\
\texttt{arcloom\_sppu.v} & Add \texttt{familiarity} input, pass to all fields & Combinational \\
\texttt{arcloom\_top} & Wire \texttt{match\_score} $\rightarrow$ \texttt{familiarity} & Wire \\
\texttt{arcloom\_axi\_wrapper.v} & Expose \texttt{match\_score} on read register & Read-only \\
\bottomrule
\end{longtable}

No clock added. No register in feedback path. All changes preserve the
SPPU's purely combinational nature.

% ============================================================
\chapter{Reference Platform: Autonomous Wheeled Robot}

\section{Purpose}

Validates ArcLoom's structural perception on real sensory data through
real krimelack transduction, processed by real fabric, producing real
motor commands.

\textbf{Modes:} Person-following, obstacle avoidance, course-following.

\section{Platform Specifications}

Chassis: 4WD, $\sim$30cm $\times$ 25cm, $<$3kg.
Drive: Differential (2 powered + 2 caster).
Battery: LiPo 3S 11.1V, 5000mAh ($\sim$2hr runtime).

\section{Config A: Pure Ternary BOM}

\begin{center}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Component} & \textbf{Part} & \textbf{Qty} \\
\midrule
FPGA & Xilinx Artix-7 XC7A200T & 1 \\
PLL Array & Si5351A & 4 \\
DAC & AD5686R quad 16-bit & 2 \\
ADC & AD7689 8-ch 16-bit & 2 \\
Stereo Camera & OV7675 dual & 1 pair \\
Depth/ToF & VL53L5CX 8$\times$8 & 2 \\
IMU & ICM-42688-P 6-axis & 1 \\
IR Proximity & VCNL4040 & 4 \\
Wheel Encoder & AS5048A magnetic & 2 \\
Motor & Pololu 37D 12V 200RPM & 2 \\
Motor Driver & DRV8874 H-Bridge & 2 \\
Camera Servo & SG90 & 1 \\
Power & TPS65281 multi-rail & 1 \\
\bottomrule
\end{tabular}
\end{center}

Fabric: 64 trit rings in 8$\times$8 lattice. Coupling matrix loaded as
fixed-point coefficients. No instruction memory.

\section{Config B: Hybrid BOM}

Same sensors and actuators. Add STM32H743 MCU (BCP). FPGA can be smaller
(XC7A100T). BCP handles sensor init, H1-C correction, binary fallback,
safety monitoring, telemetry (UART/BLE).

\section{Build Sequence}

\begin{enumerate}[label=\textbf{Phase \arabic*} (Months \arabic*--\arabic*):, start=1]
  \item[Phase 1 (Months 1--3):] FPGA simulation. Validate trit stability, parity chains, Schmitt trigger, and MathLoom global settle (exhaustive 4-trit + scaling to 32-trit).
  \item[Phase 2 (Months 3--6):] Hybrid robot. Connect sensors and motors. Validate H1-C. Demo person-following.
  \item[Phase 3 (Months 6--12):] Pure ternary. Disable BCP. Characterize noise tolerance and power.
  \item[Phase 4 (Months 12--18):] Analog fabric. Replace FPGA with physical oscillator arrays.
\end{enumerate}

% ============================================================
\chapter{Time Management}

Three clocks plus horizon:
\begin{itemize}[nosep]
  \item $t$: input time (monotonic)
  \item $k$: structural time (gate index)
  \item $\tau$: lattice time (integration steps within gate)
  \item $h$: horizon step index
\end{itemize}

Lattice steps per gate:
$N_{int}(k) = \text{clamp}(N_{min} + \text{round}(N_{range} \cdot Sched(k)),\; [N_{min}, N_{max}])$

where $Sched(k) = (1 - U^*_k) \cdot w_k \cdot (1 - N(G_k))$.

SafeMode $\Rightarrow N_{int}(k) = N_{min}$.

% ============================================================
\chapter{Comparison of Configurations}

\begin{center}
\begin{tabular}{@{}p{3.5cm}p{5cm}p{5cm}@{}}
\toprule
\textbf{Feature} & \textbf{Pure Ternary} & \textbf{Hybrid AHPP} \\
\midrule
Logic & Topological invariants & Binary-supervised phases \\
Error correction & Geometric & H1-C + binary fallback \\
Clock & Asynchronous & BCP clock + fabric \\
Power (quiet) & Near-zero & BCP idle + leakage \\
Determinism & Topological & BCP-certified \\
Certification & Novel & Standard (MCU safety case) \\
Debugging & Field observation & Register + telemetry \\
Use case & Research, cognition & Commercial, medical, auto \\
Timeline & 12--18 months & 6--9 months \\
\bottomrule
\end{tabular}
\end{center}

% ============================================================
\chapter{Invariants and Constraints (Normative)}

\begin{enumerate}
  \item Winding number is the \textbf{only} valid trit representation.
  \item $J_{ij}$ is \textbf{derived}, not fitted.
  \item Parity constants $K$ are set at configuration, never modified.
  \item $\alpha$ (Schmitt) is a frozen rational constant.
  \item BCP \textbf{never modifies} the coupling matrix.
  \item SL-1 is a hardware output, not a software flag.
  \item Krimelack $\kappa$ is frozen per sensor type.
  \item $H_{total}$ \textbf{must} be Hermitian.
  \item All interactions $W$ \textbf{must} be symmetric.
  \item Law operators $L_j$ \textbf{must} be Hermitian.
  \item Goal operators $G_g$ \textbf{must} be bounded.
  \item $P_{in}$ (MapInject) is deterministic from configuration seed.
\end{enumerate}

% ============================================================
% APPENDICES
% ============================================================

\appendix

\chapter{MathLoom: Balanced Ternary Arithmetic via Global Settling}

\textit{This appendix defines the Math Loom (ML) subsystem for exact
arithmetic on the TAL substrate. Originally conceived as a theoretical
thought experiment, analysis of the global settling property of coupled
TAL lattices suggests MathLoom may achieve practical arithmetic speeds
by exploiting physics parallelism for carry propagation. Validation is
scheduled for Phase~1 FPGA simulation alongside trit stability testing.}

\section{Concept}

Rather than using rigid binary logic gates, MathLoom represents numbers
as balanced ternary digit strings and implements arithmetic through
\textbf{constraint relaxation} in the TAL medium. Operands are injected
as biases into a coupled lattice. The lattice settles to the energy
minimum that satisfies all digit constraints simultaneously.

The key insight: the TAL lattice settles \textit{globally}, not locally.
Carry propagation is not a sequential chain --- it is a physical coupling
that resolves through the medium at the speed of oscillator interaction,
potentially producing correct results in a single settle cycle regardless
of word width.

\section{Digit Constraint}

For each digit position $i$:
\begin{equation}
  a_i + b_i + c_i = s_i + 3 \cdot c_{i+1}
\end{equation}
where $a_i, b_i$ are input digits, $s_i$ is the sum digit, and $c_{i+1}$
is the carry to the next position. All values are balanced ternary:
$a_i, b_i, s_i \in \{-1, 0, +1\}$, $c_i \in \{-1, 0, +1\}$.

\section{The Carry Problem and Three Solutions}

In binary ALUs, carry-lookahead logic computes all carries in parallel
using combinatorial AND/OR gates. In a naive MathLoom implementation,
each digit position must settle sequentially because carry $c_{i+1}$
depends on the settled state of position $i$. For an $n$-trit word,
this gives worst-case latency of $n \times t_{settle}$.

Three approaches resolve this:

\subsection{Approach 1: Ternary Carry-Lookahead Tree}

The balanced ternary carry function is associative:
\begin{equation}
  c_{i+1} = \left\lfloor \frac{a_i + b_i + c_i + 1}{3} \right\rfloor - 1
\end{equation}

This composes across digit groups. A carry-lookahead tree computes group
carries in parallel using $\lceil \log_3 n \rceil$ levels of TAL cells.

\textbf{Latency:} $\lceil \log_3 n \rceil \times t_{settle}$.
For 32 trits: $\sim$3 levels $\times$ 3~ns $=$ 9~ns.

\textbf{Assessment:} Approximately 30$\times$ slower than binary ALU.
Viable for structural computation where arithmetic is infrequent.

\subsection{Approach 2: Redundant Ternary Representation}

Allow intermediate digits to temporarily hold values in the extended set
$\{-2, -1, 0, +1, +2\}$. This eliminates carry propagation entirely:
each digit absorbs its carry locally.

\begin{equation}
  s_i' = a_i + b_i \in \{-2, \ldots, +2\}
\end{equation}

A subsequent normalization pass converts redundant digits back to
$\{-1, 0, +1\}$. Normalization is fully parallel --- every digit
normalizes independently:
\begin{equation}
  s_i = s_i' - 3 \cdot \text{round}(s_i'/3), \qquad
  c_{i+1} = \text{round}(s_i'/3)
\end{equation}

\textbf{Latency:} Two parallel settle cycles (sum + normalize).
For any word width: $\sim$2 $\times$ $t_{settle}$ $=$ 6~ns.

\textbf{Assessment:} Approximately 20$\times$ slower than binary ALU.
Independent of word width. Requires TAL cells with 5 stable basins
instead of 3 (extended TSAC).

\subsection{Approach 3: Global Lattice Settling (Primary Candidate)}

\begin{axiom}[Global Settle Hypothesis]
When all digit constraints are encoded as coupling terms in a single TAL
lattice, and both operands are injected simultaneously as bias fields,
the global energy minimization produces the correct arithmetic result in
a single settle cycle --- regardless of word width.
\end{axiom}

\textbf{Physical basis:} The TAL lattice does not ``know'' about digits
or carries. It minimizes total energy:
\begin{equation}
  E_{ML}(\mathbf{s}, \mathbf{c}; \mathbf{a}, \mathbf{b}) =
    \sum_{i=0}^{n-1} \left[ V(s_i) + V(c_i) \right]
    + \lambda_{digit} \sum_{i=0}^{n-1} (a_i + b_i + c_i - s_i - 3c_{i+1})^2
    + \lambda_{parity} \sum_{chains} \left(\sum_j w_j - K\right)^2
\end{equation}

where:
\begin{itemize}[nosep]
  \item $V(\cdot)$ is the tri-well potential (TSAC basins)
  \item $\lambda_{digit}$ is the digit-constraint coupling strength
        (frozen rational)
  \item $\lambda_{parity}$ is the parity-chain coupling (geometric
        error correction)
  \item $a_i, b_i$ are injected as fixed biases (not free variables)
\end{itemize}

The carry ``propagates'' through the coupling matrix at the speed of the
physical medium (oscillator coupling velocity), not through sequential
cell settling. The entire lattice converges simultaneously because all
constraints are applied in parallel through the energy functional.

\textbf{Latency:} $\sim$1 $\times$ $t_{settle}$ for any word width.
For 32 trits: $\sim$3~ns.

\textbf{Assessment:} If validated, this is approximately 10$\times$ slower
than binary ALU --- but \textbf{independent of word width}. A 256-trit
addition takes the same time as a 4-trit addition. Binary carry-lookahead
scales as $O(\log n)$; global settling scales as $O(1)$.

For very wide words (cryptographic, scientific), MathLoom could
potentially \textbf{match or exceed} binary ALU performance because the
binary carry tree grows logarithmically while MathLoom remains constant.

\textbf{Critical validation requirement:} Phase~1 FPGA simulation must
demonstrate that global settling produces correct 32-trit addition in a
single settle cycle. If it does not converge (oscillates or settles to
incorrect state), fall back to Approach~1 or 2.

\section{Multiplication (Profile M1)}

Multiplication of two $n$-trit numbers $A \times B$ can be decomposed
into:
\begin{enumerate}[nosep]
  \item \textbf{Partial product generation:} $n$ partial products, each
        a single-trit $\times$ $n$-trit multiplication (trit-by-word).
        Since trits are $\{-1, 0, +1\}$, this is trivial: negate, zero,
        or pass-through.
  \item \textbf{Partial product accumulation:} $n$ additions via MathLoom.
        If global settling works, all partial products can be injected
        into a single extended lattice and accumulated in one settle cycle.
\end{enumerate}

\textbf{Latency estimate (global settle):} $\sim$1--2 $\times$ $t_{settle}$
for any word width. This is speculative and requires Phase~1 validation.

\section{Division: Folding Division (Profile M2)}

The original spec proposed division via lattice constraint settling.
The implemented method is \textbf{folding division} --- a novel approach
discovered during development.

\subsection{Concept}

Standard division asks ``how many times does $B$ fit into $A$?'' ---
an iterative counting procedure. Folding division asks: \textbf{at which
fold does the field exhaust itself?}

\begin{enumerate}[nosep]
  \item Field starts with energy $|A|$ (numerator magnitude)
  \item Each fold removes $|B|$ units (denominator magnitude)
  \item When remaining field $< |B|$, it falls into the dead zone
  \item Number of folds = quotient $q$
  \item Residual energy = remainder $r$
\end{enumerate}

Formally: $A = q \cdot B + r, \quad |r| < |B|$.

\subsection{Connection to SPPU Physics}

This is the same mechanism as the SPPU dead zone. In the SPPU, input
field energy (weighted sum) either exceeds the dead-zone barrier (commits)
or doesn't (stays null). In folding division, the numerator field either
exceeds the denominator (sustains another fold) or doesn't (falls into
the dead zone). The SPPU IS a divider --- input energy divided by coupling
structure. \texttt{arcloom\_mathloom\_div} makes this explicit as
standalone arithmetic.

\subsection{Fractional Division}

To compute $A/B$ with $N$ fractional digits: left-shift $A$ by $N$
positions (multiply by $3^N$ --- append $N$ null trits, zero cost). Fold.
The quotient's lower $N$ digits are the fractional part.
Truncation-as-rounding guarantees these are the optimal $N$-digit
approximation. No correction pass.

$1/3$ is exact in balanced ternary: $(+1) \cdot 3^{-1}$. Impossible in
binary (infinite repeating fraction).

\subsection{Implementation}

Implemented in \texttt{arcloom\_mathloom\_div.v} as a 2-state FSM
(IDLE $\rightarrow$ FOLDING). Each fold is one clock cycle. Uses
\texttt{arcloom\_bt\_compare} for magnitude check and
\texttt{arcloom\_bt\_adder} for subtraction. Worst case for 4-trit
operands ($\pm 40$): 40 cycles.

\subsection{Comparison}

Comparison is a special case of subtraction: compute $A - B$ via
\texttt{arcloom\_bt\_sub}, scan from MSB for the first non-null trit.
That trit's sign determines greater/less/equal. Purely combinational.

\subsection{Verification}

\begin{itemize}[nosep]
  \item Folding division: 41,430 simulation tests, zero errors
  \item Folding division on silicon: 18/18 tests, zero errors
  \item Comparison on silicon: 6,561/6,561 exhaustive, zero errors
\end{itemize}

\section{Safety}

If the lattice fails to settle within $T_{settle,max}$ or repair cycles
exceed $R_{max}$, the output is \textbf{Neutral} (Valid=0) --- not a
wrong answer. The system fails gracefully rather than silently producing
incorrect arithmetic.

\section{MathLoom Validation Results}

Phase~1 validation is \textbf{complete}. All operations verified on
Xilinx Zynq-7020 FPGA silicon (PYNQ-Z2), April 2026:

\begin{longtable}{@{}llrl@{}}
\toprule
\textbf{Operation} & \textbf{Module} & \textbf{Tests} & \textbf{Errors} \\
\midrule
\endhead
Addition       & \texttt{arcloom\_bt\_adder}   & 6,561  & 0 \\
Multiplication & \texttt{arcloom\_trit\_mul}    & 6,561  & 0 \\
Comparison     & \texttt{arcloom\_bt\_compare}  & 6,561  & 0 \\
Division (sim) & \texttt{arcloom\_mathloom\_div} & 41,430 & 0 \\
Division (silicon) & \texttt{arcloom\_mathloom\_div} & 18 & 0 \\
\midrule
\textbf{Total} & & \textbf{61,131} & \textbf{0} \\
\bottomrule
\end{longtable}

\textbf{Computational completeness:} Addition + multiplication + folding
division = any numerical function via iteration. Fractions, square roots,
and trigonometric functions verified in simulation through folding and
Newton iteration.

\textbf{Implementation:} Addition, multiplication, and comparison are
purely combinational ($\sim$10--15\,ns for 4-trit operands on Zynq-7020).
Division is the sole clocked MathLoom module (2-state FSM, one fold per
clock cycle). MathLoom exists at I/O boundaries only --- not used inside
the SPPU settling path.

\section{Significance}

MathLoom is validated on silicon with zero errors across 61,131 tests.
It represents a fundamentally different approach to arithmetic:
\begin{itemize}[nosep]
  \item \textbf{Constraint satisfaction:} Each digit position satisfies
        $a_i + b_i + c_i = s_i + 3 c_{i+1}$. The hardware stores the
        constraint, not an algorithm. The answer is the unique solution.
  \item \textbf{No instruction set required:} Arithmetic is a consequence
        of constraint propagation through LUTs, not instruction execution.
  \item \textbf{Truncation equals rounding:} Balanced ternary truncation
        rounds to nearest, not toward zero. No bias accumulation.
  \item \textbf{Folding division:} Novel method connecting division to
        the SPPU's dead-zone settling. Same physics --- force vs barrier,
        iterated until exhaustion.
  \item \textbf{Boundary role:} MathLoom exists at I/O boundaries (BSIL
        conversion, actuator output, external communication). The SPPU
        settling path uses weighted accumulation and dead-zone thresholding,
        not MathLoom arithmetic.
\end{itemize}

MathLoom is promoted from theoretical appendix to \textbf{proven core
capability} as of April 2026.

% ============================================================
\chapter{Risk Register}

\begin{longtable}{@{}p{1cm}p{3.5cm}p{5cm}p{4cm}@{}}
\toprule
\textbf{ID} & \textbf{Risk} & \textbf{Impact} & \textbf{Mitigation} \\
\midrule
\endhead
R1 & 0-basin instability & Neutral state ($w=0$) not stable under noise;
      ternary collapses to binary & Domain pinning geometry;
      Schmitt trigger; validate with 27-cell tile \\
R2 & Settle time too slow & TAL relaxation exceeds real-time requirements &
     Quantify in Phase 1 FPGA sim; bound $N_{int}$ \\
R3 & Manufacturing variance & Tri-well margins too tight for
     production & Parity chains; BCP compensation (hybrid) \\
R4 & Collective oscillation & Large coupled arrays exhibit emergent
     dynamics & Staged scaling; 27-cell $\to$ 64-cell $\to$ 256-cell \\
R5 & BSIL capture completeness & Insufficient observables to reproduce
     binary workflow & Validate with known workflows; define minimum
     observable set \\
R6 & Ecosystem adoption & No tooling, no developers, no community &
     Hybrid mode provides familiar MCU interface; WeaveSpec is JSON \\
R7 & MathLoom global settle failure & Carry does not propagate through
     coupling; arithmetic requires sequential settling &
     Fall back to Approach 1 (carry tree) or 2 (redundant representation);
     validate in Phase 1 with width-independence test \\
\bottomrule
\end{longtable}

% ============================================================
\chapter{Version History}

\begin{longtable}{@{}lll@{}}
\toprule
\textbf{Version} & \textbf{Date} & \textbf{Description} \\
\midrule
\endhead
v0.3 & 2026-01-06 & Original $\psi$-lattice architecture, Law-Fields, Krimelacks memory \\
v0.4 & 2026-01-06 & Locked OD-1 through OD-6, MapInject, commit mechanics \\
BSIL v0.1 & 2026-01-06 & Binary Story Ingestion Layer \\
WeaveSpec v0.1 & 2026-01-06 & Declarative programming surface \\
v1.0 & 2026-01-06 & Consolidated spec with WVB, TDM, conformance indicators \\
v1.1 & 2026-01-07 & Binary-free pivot, five BF compliance rules \\
v1.2 & 2026-01-07 & Ternary differential signaling, performance metrics, ``worth it'' analysis \\
v1.3 & 2026-01-07 & TAL core (tri-stable attractor cells), 27-cell test tile \\
v1.4 & 2026-01-07 & MathLoom addendum (balanced ternary arithmetic) \\
v4.0 & 2026-04-10 & Physical implementation: triple-node rings, Schmitt trigger, parity chains,
                     krimelack I/O, robot BOM \\
\textbf{v5.0} & \textbf{2026-04-10} & \textbf{Master Canon.} Consolidates all prior specs. Supersedes all. \\
v5.0.1 & 2026-04-10 & MathLoom upgraded: global settle hypothesis, carry-lookahead \\
       &            & tree, redundant ternary, multiplication sketch, validation protocol. \\
       &            & MathLoom promoted from theoretical appendix to Phase~1 validation target. \\
v5.1 & 2026-05-03 & Familiarity Feedback: clockless habituation via krimelack \\
     &            & dead-zone coupling. Biological principle, FPGA implementation, \\
     &            & TSAC substrate fatigue, loop stability, cognitive implications. \\
     &            & MathLoom updated: folding division (41,430 tests), validation \\
     &            & results (61,131 total, zero errors), promoted from appendix \\
     &            & to proven core capability. \\
\bottomrule
\end{longtable}

\vspace{2em}
\hrule
\vspace{0.5em}
{\color{al-gray}\small This document is confidential and for internal use only.
It constitutes the master specification for the ArcLoom Processor
Architecture. All prior ArcLoom specifications are superseded by this
document. The $\psi$-lattice architecture, Law-Field programming model,
Krimelacks memory, BSIL interoperability, and WeaveSpec programming
surface are the canonical layers. The physical implementation (TAL cells,
triple-node rings, parity chains) is the reference hardware design. All
mathematics are deterministic. All constants are frozen rationals or
derived from natural mathematical constants. No parameters are fitted,
estimated, or heuristically determined.}

\end{document}
