% ============================================================
%  ArcLoom SPPU Architecture Specification
%  Version 1.3 — May 2026
%  Confidential — Internal Use Only
% ============================================================
\documentclass[11pt, a4paper]{article}

\usepackage[margin=2.2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{graphicx}

\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue}

\definecolor{tfe-gold}{RGB}{180, 140, 60}
\definecolor{tfe-dark}{RGB}{30, 30, 30}
\definecolor{tfe-gray}{RGB}{100, 100, 100}

\pagestyle{fancy}
\fancyhf{}
\rhead{\textcolor{tfe-gray}{\small ArcLoom SPPU Architecture v1.3}}
\lhead{\textcolor{tfe-gray}{\small Confidential --- Internal Use Only}}
\rfoot{\textcolor{tfe-gray}{\small Page \thepage}}

\titleformat{\section}{\large\bfseries\color{tfe-dark}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries\color{tfe-dark}}{}{0em}{}
\titleformat{\subsubsection}{\normalsize\itshape\color{tfe-dark}}{}{0em}{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

\begin{center}
  {\LARGE \textbf{ArcLoom SPPU}}\\[6pt]
  {\large Architecture Specification}\\[4pt]
  {\large Fixed-Weight Ternary Classifier with Native Uncertainty}\\[8pt]
  {\color{tfe-gray}\small Version 1.3 \quad|\quad May 2026 \quad|\quad Confidential}\\[4pt]
  {\color{tfe-gray}\small Joseph Forrester \quad|\quad DSF-AI Architecture}
\end{center}

\vspace{1em}
\hrule
\vspace{1em}

% ============================================================
\section{What This Is}

The ArcLoom SPPU is a fixed-weight combinational classifier
implemented in balanced ternary ($-1, 0, +1$) logic. It is
architecturally a feedforward threshold network --- comparable
to a single-hidden-layer perceptron --- with one critical
difference: the null output state ($0$) is a first-class
architectural result representing genuine structural uncertainty,
not a failure to classify.

The SPPU computes. It is a circuit. We do not claim otherwise.

What distinguishes it from prior perceptron implementations:
\begin{enumerate}[nosep]
  \item \textbf{Native three-state output:} Each output trit
        produces $+1$, $-1$, or $0$ (dead zone). The dead zone
        is not a design artifact --- it is the system's honest
        statement that the input evidence is insufficient to
        commit this dimension. No conventional binary or ternary
        classifier architecture treats uncommitted output as a
        first-class result.
  \item \textbf{Balanced ternary encoding:} Sensor inputs are
        encoded as 8-trit balanced ternary values via BSIL-BT.
        The coupling weights are the positional values $3^i$,
        which means the weighted sum \textbf{reconstructs the
        original sensor value} from its BT encoding. This is
        the definition of positional notation --- not a discovery,
        but a deliberate architectural choice that eliminates
        quantization loss in the encoding-to-coupling path.
  \item \textbf{Per-strand signed polarity:} The $3^i$ magnitude
        weights are fixed by the encoding. Selectivity comes from
        the \textbf{sign} applied per strand per decision field.
        For example, the steer decision uses $+3^i$ for the left
        sensor and $-3^i$ for the right sensor. The magnitude
        reconstructs; the sign couples. These are different
        functions and should not be conflated.
  \item \textbf{Zero dynamic power between evaluations:} The
        decision path is purely combinational with no clock.
        Power consumption is zero between sensor events. This
        is shared with any combinational logic block; the
        contribution here is that the classifier function is
        useful enough to justify a dedicated ASIC.
  \item \textbf{Structural memory (Krimelack):} A content-addressable
        motif store provides cue-based recall. Match scores feed
        back into the dead zone, raising the commitment barrier
        for familiar states. This provides clockless habituation
        without timers.
\end{enumerate}

\textbf{What this is not:} This is not a general-purpose processor.
It does not execute instructions. It is not programmable in the
conventional sense. It is a fixed-function sensor classifier with
configurable parameters (baselines, dead zones, strand polarities)
set by an external calibration service (DSF-AI). It is comparable
in scope to a neuromorphic classifier tile, not to a CPU or GPU.

% ============================================================
\section{Relation to Prior Art}

\subsection{Perceptron Comparison}

The local field computation for each output trit is:
\begin{equation}
  h_j = \sum_{i} s_k \cdot w_i \cdot t_i + h_j^{ext}
\end{equation}
where $w_i = 3^{i \bmod 8}$ is the positional weight (fixed),
$s_k \in \{-1, 0, +1\}$ is the per-strand sign for decision
field $j$ (configured by DSF-AI), and $t_i \in \{-1, 0, +1\}$
is the input trit value.

The activation function is a three-way threshold:
\begin{equation}
  t_j = \begin{cases}
    +1 & \text{if } h_j > \tau_j \\
    -1 & \text{if } h_j < -\tau_j \\
    0  & \text{if } |h_j| \leq \tau_j
  \end{cases}
\end{equation}

This is structurally a perceptron with a dead band. We acknowledge
the prior art. The differences that justify a dedicated architecture
are:

\begin{itemize}[nosep]
  \item The dead band produces a \textbf{three-valued output}
        where the third value means ``insufficient evidence.''
        A standard perceptron produces a binary decision regardless
        of input ambiguity.
  \item The weights factor into \textbf{fixed magnitude} ($3^i$,
        determined by the number system) and \textbf{configurable
        sign} ($s_k$, determined by the application). This
        separation means the classifier can be reconfigured for
        different sensor arrangements without changing the
        arithmetic hardware.
  \item The balanced ternary encoding provides \textbf{free rounding}
        via truncation and \textbf{trivial negation} via bit-swap,
        both of which simplify the hardware.
  \item The Krimelack feedback loop provides \textbf{clockless
        habituation} --- the dead zone rises for repeated patterns
        without any timer or counter.
\end{itemize}

\subsection{Neuromorphic Comparison}

The appropriate comparison class is neuromorphic silicon, not
general-purpose processors. Per-event energy comparison:

\begin{center}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Architecture} & \textbf{Per-event energy} & \textbf{Latency} & \textbf{Uncertainty} \\
\midrule
Intel Loihi 2 & $\sim$100 pJ/spike & $\sim$1 $\mu$s & Encoded as rate \\
IBM TrueNorth & $\sim$26 pJ/spike & $\sim$1 ms (tick) & Probabilistic \\
SpiNNaker 2 & $\sim$10 nJ/inference & $\sim$1 ms & Encoded as rate \\
\textbf{SPPU tile} & $\sim$0.1--1 pJ/event & $\sim$5--10 ns & \textbf{Native (null trit)} \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Caveats:} The SPPU energy estimate includes only the
combinational decision path. It excludes BSIL encoding (clocked,
BRAM access), Krimelack recall (combinational but larger), and
any host interface. A like-for-like comparison requires measuring
the complete sensor-to-decision path on the FPGA prototype, which
has not yet been done. The table above is an estimate, not a
measurement. We will not claim a specific power advantage until
measured.

The SPPU latency advantage (ns vs $\mu$s--ms) is architectural:
combinational evaluation has no tick/timestep overhead. This is
verifiable on the FPGA prototype via propagation delay measurement.

The uncertainty representation is the clearest architectural
distinction. Neuromorphic systems encode uncertainty as spike rate
or probability. The SPPU's null trit is a discrete, deterministic
signal: the classifier did not have enough evidence to commit.
This is qualitatively different from ``low confidence'' --- it is
a hardware-level admission of ignorance.

% ============================================================
\section{SPPU Tile}

\subsection{Architecture}

Each SPPU tile is a combinational classifier. No clock input.
The output appears within one propagation delay of the inputs
changing.

\textbf{Trit encoding:} 2 wires per trit.
\begin{itemize}[nosep]
  \item \texttt{00} = 0 (null / uncommitted / dead zone)
  \item \texttt{01} = +1 (positive / excite)
  \item \texttt{10} = -1 (negative / inhibit)
  \item \texttt{11} = invalid (never produced)
\end{itemize}

\subsection{Strand Configuration (FPGA-Proven, 12-Strand)}

12 input strands $\times$ 8 trits + 2 settling $\times$ 3 trits
+ 1 decision $\times$ 3 trits = 105 trits = 210 wires per SPPU.

\begin{center}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{\#} & \textbf{Strand} & \textbf{Trits} & \textbf{Type} & \textbf{Source} \\
\midrule
0  & Front distance     & 8 & Input    & BSIL-BT (IR, baseline 80) \\
1  & Front direction    & 8 & Input    & BSIL-BT (1st derivative) \\
2  & Front acceleration & 8 & Input    & BSIL-BT (2nd derivative) \\
3  & Left distance      & 8 & Input    & BSIL-BT (IR, baseline 111) \\
4  & Right distance     & 8 & Input    & BSIL-BT (IR, baseline 144) \\
5  & Camera Y upper     & 8 & Input    & BSIL-BT (brightness upper half, baseline 180) \\
6  & Camera Y lower     & 8 & Input    & BSIL-BT (brightness lower half, baseline 180) \\
7  & Camera edge upper  & 8 & Input    & BSIL-BT (texture upper half, baseline 145) \\
8  & Camera edge lower  & 8 & Input    & BSIL-BT (texture lower half, baseline 145) \\
9  & Camera U upper     & 8 & Input    & BSIL-BT (chrominance upper half, baseline 121) \\
10 & Camera U lower     & 8 & Input    & BSIL-BT (chrominance lower half, baseline 121) \\
11 & Structural density & 8 & Input    & BSIL-BT (high-edge lines/frame, baseline 145) \\
   & Context            & 3 & Settling & Coupled from 96 input trits \\
   & Momentum           & 3 & Settling & Coupled from 96 input trits \\
   & Decision           & 3 & Output   & Coupled from 102 trits (96 + 6 settling) \\
\bottomrule
\end{tabular}
\end{center}

Camera baselines derived from room measurement: Y=180, edge=145,
U=121. These are calibrated values from DSF-AI, not design
parameters.

\subsection{Coupling Network}

Two-level feedforward combinational circuit.

\textbf{Level 1 (parallel):} Context and Momentum each compute
3 trits from 96 input trits (12 strands $\times$ 8 trits) via
weighted summation with dead-zone thresholding. 6 local field
instances, each with 96 inputs.

\textbf{Level 2:} Decision computes 3 trits from 102 trits
(96 input + 6 settling) via weighted summation with dead-zone
thresholding. 3 local field instances, each with 102 inputs.

\textbf{Weight structure:} Each local field computes:
\begin{equation}
  h_j = \sum_{k=0}^{N_{strands}-1} s_{k,j} \cdot
        \sum_{i=0}^{7} 3^i \cdot t_{k,i} + h_j^{ext}
\end{equation}

The inner sum ($\sum 3^i t_{k,i}$) reconstructs the sensor value
from its BT encoding. The outer sign ($s_{k,j}$) determines how
that sensor couples to decision field $j$. For example:

\begin{center}
\begin{tabular}{@{}lrrr@{}}
\toprule
\textbf{Strand} & \textbf{Steer ($s_{k,0}$)} & \textbf{Speed ($s_{k,1}$)} & \textbf{Conf ($s_{k,2}$)} \\
\midrule
Front distance   & 0      & $+1$   & $+1$ \\
Front direction  & 0      & $-0.5$ & $+1$ \\
Left distance    & $+1$   & 0      & $+1$ \\
Right distance   & $-1$   & 0      & $+1$ \\
Camera Y upper   & 0      & 0      & $+1$ \\
Camera edge upper & 0     & 0      & $+1$ \\
\vdots           & \vdots & \vdots & \vdots \\
\bottomrule
\end{tabular}
\end{center}

The steer decision uses opposite signs for left ($+1$) and right
($-1$), producing a differential signal that distinguishes ``wall
on left'' from ``wall on right.'' This is not ``all sensors
weighted equally'' --- the per-strand sign IS the selectivity.
The $3^i$ magnitude is the encoding fidelity. They serve different
functions.

The $-0.5$ on front direction in the speed field is a damping
term: direction spikes (transients) oppose the distance signal,
preventing oscillation. Only persistent distance changes drive
speed decisions.

Camera strands currently couple to confidence only ($s_{k,2} = +1$)
with zero weight for steer and speed. DSF-AI calibration will
determine whether camera features should also modulate steer
(e.g., visual asymmetry) or speed (e.g., target proximity).
These signs are configurable parameters, not architectural
constants.

\subsection{Dead Zones}

\begin{center}
\begin{tabular}{@{}lrl@{}}
\toprule
\textbf{Field} & \textbf{$\tau$ (ADC units)} & \textbf{Rationale} \\
\midrule
Context    & 500  & Calibrated to XADC noise floor \\
Momentum   & 500  & Same noise floor \\
Steer      & 250  & Lower for responsiveness \\
Speed      & 500  & Moderate damping \\
Confidence & 1000 & High bar for conviction \\
\bottomrule
\end{tabular}
\end{center}

Dead zones are calibration parameters derived by DSF-AI from
sensor noise characterization. They are not arbitrary --- they
represent the measured noise floor below which sensor signals
are structurally ambiguous. The dead zone IS the null trit's
physical meaning: ``the signal has not exceeded the noise.''

\subsection{Gate Count Estimate (12-Strand, 8-Trit)}

\begin{center}
\begin{tabular}{@{}lr@{}}
\toprule
\textbf{Component} & \textbf{Equivalent Gates} \\
\midrule
Level 1: 6 local field units (96 inputs each) & 7,200 \\
Level 2: 3 local field units (102 inputs each) & 3,800 \\
Dead-zone comparators (9 total) & 200 \\
Input/output buffers & 100 \\
\midrule
\textbf{Total per SPPU tile} & \textbf{$\sim$11,300} \\
\bottomrule
\end{tabular}
\end{center}

Gate count scales linearly with strand count $\times$ trit width.
The 12-strand 8-trit configuration is $\sim$5$\times$ larger than
the original 5-strand 3-trit design.

\subsection{Power Analysis}

\textbf{Decision path only} (combinational, no clock):
\begin{equation}
  P_{event} \approx N_{gates} \times C_{wire+gate} \times V_{dd}^2
\end{equation}

Using $N_{gates} = 200$ (average switching per event),
$C_{wire+gate} = 5$ fF (gate + local wire in 7nm), $V_{dd} = 0.7$ V:
\begin{equation}
  P_{event} \approx 200 \times 5\text{fF} \times 0.49 \approx 490\text{ fJ/event}
\end{equation}

This estimate includes local wire capacitance (5$\times$ gate
capacitance), which was omitted in v1.2.

\textbf{BSIL encoding} (clocked): $\sim$10 pJ per sample
(BRAM read + baseline subtraction + derivative computation).

\textbf{Total sensor-to-decision:} $\sim$10.5 pJ at 7nm.
At 1 kHz sample rate: $\sim$10.5 nW per tile.

\textbf{Comparison:} Loihi 2 at $\sim$100 pJ/spike. The SPPU is
$\sim$10$\times$ lower energy per event, not 10$^9\times$. The
v1.2 claim of 10$^9\times$ versus Cortex-M0 was a misleading
comparison against a general-purpose processor performing a
different function.

\subsection{Timing}

Propagation delay for the 12-strand configuration in 7nm:
\begin{itemize}[nosep]
  \item Level 1 (96-input weighted sum + threshold): $\sim$5 ns
  \item Level 2 (102-input weighted sum + threshold): $\sim$6 ns
  \item Total input-to-decision: $\sim$11 ns
\end{itemize}

These are estimates based on gate-level fanout analysis. FPGA
propagation delay has not been measured. We intend to measure
this on the PYNQ prototype using input stimulus timing versus
output transition, and will report measured values in a future
revision.

% ============================================================
\section{MathLoom Arithmetic Unit}

\subsection{Architecture}

MathLoom provides balanced ternary arithmetic for BSIL encoding,
threshold computation, and general-purpose calculation. The core
ALU (add, multiply, compare) is combinational. The divider is
clocked (iterative folding).

\textbf{Verified operations:}
\begin{center}
\begin{tabular}{@{}lllr@{}}
\toprule
\textbf{Operation} & \textbf{Method} & \textbf{Tests} & \textbf{Failures} \\
\midrule
12-trit addition     & Ripple-carry          & 6,561  & 0 \\
12-trit multiplication & Shift-and-add       & 6,561  & 0 \\
12-trit comparison   & Subtraction + MSB     & 6,561  & 0 \\
12-trit division     & Folding (iterative)   & 6,480  & 0 \\
Complex division     & Paired folding        & 14,520 & 0 \\
Matrix inversion     & Element-wise folding  & 6,016  & 0 \\
Polynomial division  & Synthetic folding     & 14,406 & 0 \\
Edge cases           & Division by $\pm$1, 0 & 8      & 0 \\
\midrule
\textbf{Total}       &                       & \textbf{41,430} & \textbf{0} \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Key Properties}

\textbf{Truncation = rounding:} In balanced ternary, truncating
to $N$ digits automatically rounds to the nearest representable
value. Binary requires explicit rounding logic.

\textbf{Folding division:} Iterative subtraction with native
rounding. The remainder is a first-class output (not discarded
as in floating-point division). $1/3$ is exact in balanced
ternary.

\textbf{Computational completeness:} Addition, multiplication,
and folding division form a complete arithmetic basis. Square
roots via Newton iteration, trigonometric functions via Taylor
series or CORDIC — all verified in simulation.

% ============================================================
\section{BSIL-BT — Binary Sensor Ingestion Layer}

Converts binary sensor data to balanced ternary trit strands.

\textbf{Encoding:} Per-sensor baseline subtraction, clamp to
$\pm$3280 (8-trit BT range), BRAM ROM lookup for BT conversion.
First and second derivatives computed from consecutive samples.

\textbf{Baselines} are configurable parameters set by DSF-AI
calibration. Current FPGA values (measured from room background):
\begin{itemize}[nosep]
  \item IR sensors: front=80, left=111, right=144
  \item Camera: Y=180, edge=145, U=121
\end{itemize}

BSIL-BT is the \textbf{only clocked component} in the
sensor-to-decision path. It runs at the sensor sample rate
(not a system clock). Between samples, dynamic power is zero.

For the ASIC, baselines should be register-writable so DSF-AI
can reconfigure at runtime without re-synthesis.

% ============================================================
\section{Krimelack — Structural Memory}

Content-addressable motif store. 32 entries $\times$ 48 bits
(24 trits) + 8-bit hash for duplicate detection.

\textbf{Autonomous commit:} Triggered by L6 structural lock,
gated by uncertainty ($U^* \leq 0.35$) and resonance
($R \geq 0.72$) derived from L6 dimensional metrics. No
external dependencies.

\textbf{Forced commit:} Software-triggered via AXI register
for calibration capture (turntable learning). Duplicate
detection still enforced.

\textbf{Recall:} Parallel comparison of current loom state
against all stored motifs. Returns best match score. Score
feeds back into SPPU dead zones via damped familiarity —
familiar states raise the commitment barrier. This provides
clockless habituation: repeated patterns become harder to
commit, forcing the system toward novel states.

% ============================================================
\section{L6 — Dimensional Collapse Observer}

Purely combinational. Counts non-null trits in the loom state.
Fires structural lock when the count exceeds a threshold.

Current FPGA: 105 trits, threshold at $105/e \approx 39$ trits
remaining (66 collapsed).

\textbf{On the threshold:} The $n/e$ value is derived from
the inflection point of the unit-ball volume function in
$n$-dimensional space ($V_n \propto \pi^{n/2} / \Gamma(n/2+1)$),
where the volume begins to decrease faster than it increases
with each additional constrained dimension. This is a
mathematical property of high-dimensional geometry, not an
arbitrary parameter.

However, the application of this threshold to a balanced
ternary state vector is an \textbf{architectural hypothesis},
not a proven physical necessity. The threshold may need
adjustment based on empirical testing. We present it as a
principled starting point, not as a derived certainty.

% ============================================================
\section{Familiarity Feedback}

\subsection{CMOS Implementation (Current)}

Krimelack match score feeds back into the SPPU dead zone:
\begin{equation}
  \tau_{\text{eff}} = \tau_{\text{base}} + f(\text{match\_score})
\end{equation}

Damped: score changes must exceed a barrier (currently 15 units)
to propagate. Prevents oscillation from small score fluctuations.

\subsection{Speculative: Ferroelectric Substrate Habituation}

\textit{This subsection describes a speculative future direction.
No hardware implementation exists. No process technology has
been identified. This is NOT part of the current architecture.}

On a ferroelectric substrate (e.g., HfO$_2$-based FeFET), sustained
polarization causes dielectric fatigue — the switching barrier
rises with repeated identical state. This could provide per-trit
habituation as a free physical property, eliminating the need for
Krimelack feedback for local adaptation.

\textbf{Open concerns:} Ferroelectric fatigue is traditionally a
reliability failure mode, not a designed computational primitive.
Endurance limits ($10^9$--$10^{12}$ cycles), retention drift,
imprint, and device-to-device variation would need to be
characterized and controlled. This remains a research question.

% ============================================================
\section{Architectural Separation: Razor and Blade}

ArcLoom (razor) and DSF-AI (blade) are distinct systems with a
clean interface.

\subsection{ArcLoom (Razor) — Fixed Hardware}

\begin{itemize}[nosep]
  \item BSIL-BT: sensor encoding (configurable baselines)
  \item SPPU: combinational classifier (configurable strand signs,
        dead zones)
  \item Krimelack: structural memory (autonomous + forced commit)
  \item L6: dimensional collapse observer
  \item MathLoom: balanced ternary ALU
\end{itemize}

The razor functions independently once configured. It does not
require DSF-AI for real-time operation.

\subsection{DSF-AI (Blade) — Calibration Service}

\begin{itemize}[nosep]
  \item Derives baselines from sensor background measurements
  \item Derives dead zones from sensor noise characterization
  \item Derives per-strand sign polarities from calibration data
  \item Runs on cloud (production) or locally (demo/embedded)
  \item Configures razor via register writes (AXI, I2C, or SPI)
\end{itemize}

\subsection{What DSF-AI Derives (Clarification)}

The $3^i$ magnitude weights are \textbf{not derived} — they are
determined by the balanced ternary number system. What DSF-AI
derives:
\begin{itemize}[nosep]
  \item \textbf{Baselines:} what ``no signal'' looks like for each
        sensor (e.g., room background Y=180)
  \item \textbf{Dead zones:} the noise floor below which signals
        are structurally ambiguous
  \item \textbf{Strand sign polarities:} which sensors contribute
        positively, negatively, or not at all to each decision field
  \item \textbf{External field biases:} static offsets (e.g., the
        $-800$ forward speed bias = ``go forward when idle'')
\end{itemize}

The razor without the blade is a combinational classifier with
default parameters. The blade makes it application-specific.
This is a viable razor/blade business model — the chip is general,
the calibration is the value-add.

% ============================================================
\section{Intellectual Property}

\subsection{Patentable Claims}

\begin{enumerate}[nosep]
  \item Combinational ternary classifier with dead-zone null output
  \item BSIL-BT: binary-to-balanced-ternary sensor encoding via
        BRAM lookup with configurable baseline
  \item Krimelack: content-addressable structural memory with
        commit gating and clockless habituation feedback
  \item L6: dimensional collapse detection via non-null trit counting
  \item Folding division: iterative BT division with native rounding
  \item MathLoom: complete balanced ternary ALU (add, multiply,
        divide, compare) on FPGA/ASIC
\end{enumerate}

\subsection{Trade Secret (DSF-AI, Separate Project)}

\begin{enumerate}[nosep]
  \item Calibration methodology (baseline, dead zone, polarity derivation)
  \item UF pipeline (L0--L4) internal algorithms
  \item Weight mapping from DSF output to strand configuration
\end{enumerate}

The FPGA/ASIC contains no trade secret code. The hardware is
fully disclosed. The trade secret is the calibration methodology,
not the classifier hardware.

% ============================================================
\section{Validation Status}

\begin{center}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Claim} & \textbf{Status} & \textbf{Evidence} \\
\midrule
BT arithmetic (add/mul/cmp) & \textbf{Proven} & 19,683 on FPGA, 0 errors \\
Folding division & \textbf{Proven} & 41,430 tests, 0 errors \\
BSIL-BT encoding & \textbf{Proven} & 12 instances on FPGA \\
Combinational classification & \textbf{Proven} & Live sensor on FPGA \\
Autonomous obstacle avoidance & \textbf{Proven} & 351 samples, 176s floor test \\
Camera in classifier (BT strands) & \textbf{Proven} & 12-strand, Y/edge/U on FPGA \\
Krimelack commit/recall & \textbf{Proven} & 32 motifs, force commit via AXI \\
L6 structural lock & \textbf{Proven} & 105-trit, KNEE=39 on FPGA \\
Motor actuation from decisions & \textbf{Proven} & TB6612FNG, 4 directions \\
\midrule
Propagation delay measurement & \textbf{Not done} & Planned \\
Per-event energy measurement & \textbf{Not done} & Planned \\
Object recognition via Krimelack & \textbf{In progress} & Preliminary data, noisy \\
Inter-SPPU coupling & \textbf{Not built} & Architecture defined only \\
\bottomrule
\end{tabular}
\end{center}

% ============================================================
\section{Security Considerations}

\subsection{Side-Channel Exposure}

The SPPU is deterministic and combinational. Identical inputs
produce identical outputs with identical timing. This means:
\begin{itemize}[nosep]
  \item Power consumption correlates with input Hamming weight
  \item Propagation delay correlates with input pattern
  \item EM emissions correlate with switching activity
\end{itemize}

For applications where sensor state is sensitive (medical
implants, security systems), these channels leak information.
Countermeasures for sensitive applications:
\begin{itemize}[nosep]
  \item Random dead-zone jitter (adds noise to timing)
  \item Balanced encoding (constant switching activity)
  \item Shielding (standard EM countermeasure)
\end{itemize}

For the current demo platform (obstacle avoidance robot), side
channels are not a concern. For Tier 2 medical/safety
applications, a threat model must be developed before deployment.

\subsection{Glitch Propagation}

Combinational logic is susceptible to glitches (transient
incorrect outputs during input transitions). In synchronous
designs, flip-flops filter glitches. The SPPU has no flip-flops
in the decision path.

\textbf{Mitigation:} The dead zone provides natural glitch
immunity — a transient that does not exceed $\tau$ produces no
output change. For signals near the dead-zone boundary, a
glitch could momentarily flip a trit. The motor control outputs
are latched (registered in the AXI wrapper), which filters
sub-cycle glitches before they reach actuators.

% ============================================================
\section{What This Specification Does Not Cover}

This document describes the SPPU architecture as validated on
FPGA. It is \textbf{not} a fabrication-ready ASIC specification.
The following are required for tape-out and are not included:

\begin{itemize}[nosep]
  \item Complete AXI register map
  \item Reset, scan, JTAG, BIST, DFT strategy
  \item PVT corners and operating points
  \item FIT rate and reliability targets
  \item SEU/SET analysis and mitigation
  \item Clock domain crossing specification
  \item Power delivery and thermal analysis
  \item Pin count and package selection
  \item Process node selection and PDK commitment
  \item Yield model and defect coverage
  \item Formal verification of dead-zone boundary behavior
  \item Concrete benchmarks against named competitors on shared tasks
\end{itemize}

These will be addressed in a separate ASIC Implementation
Specification when a fabrication partner and process node are
selected.

% ============================================================
\section{Development Roadmap}

\begin{center}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Phase} & \textbf{Status} & \textbf{Deliverable} \\
\midrule
FPGA proof of concept & Complete & PYNQ-Z2, 19,683 ops \\
Direct HW sensor path & Complete & XADC, zero CPU \\
Multi-sensor + camera  & Complete & 12-strand, 105-trit loom \\
Structural recognition & In progress & Krimelack + camera motifs \\
Object fetch demo      & Planned & Turntable capture, hunt \\
Propagation delay measurement & Planned & ns-scale timing data \\
Energy measurement     & Planned & pJ-scale per-event data \\
ASIC implementation spec & Future & Fabrication-ready document \\
Tape-out               & Future & Shuttle run \\
\bottomrule
\end{tabular}
\end{center}

% ============================================================
\section{Version History}

\begin{center}
\begin{tabular}{@{}lp{10cm}@{}}
\toprule
\textbf{Ver.} & \textbf{Changes} \\
\midrule
1.0 & Initial FPGA-validated architecture. \\
1.1 & Familiarity feedback. Folding division verified. \\
1.2 & $3^i$ coupling. Camera in SPPU. BSIL-BT. TFE removed.
      12-strand configuration. L6 updated. \\
1.3 & \textbf{Complete rewrite in response to technical review.}
      Honest framing: SPPU is a fixed-weight ternary classifier,
      not ``not computing.'' Prior art acknowledged (perceptron
      with dead band). $3^i$ claim clarified: magnitude is
      positional notation (not a discovery), selectivity comes
      from per-strand sign (configurable). Power comparison
      redone against neuromorphic silicon (Loihi, TrueNorth)
      with wire capacitance included; 10$\times$ advantage, not
      10$^9\times$. L6 threshold presented as architectural
      hypothesis, not derived certainty. TSAC moved to
      speculative appendix. Strand widths corrected throughout
      (12$\times$8 = 96 input trits, not 15 or 40). Gate counts
      recalculated for 12-strand configuration. Side-channel
      analysis added. Glitch propagation addressed. Missing ASIC
      content explicitly listed as out-of-scope. Comparison
      tables redone against neuromorphic class. IP strategy
      clarified: $3^i$ magnitudes fixed, strand signs and
      baselines are what DSF-AI derives. Security considerations
      section added. \\
\bottomrule
\end{tabular}
\end{center}

\vspace{2em}
\hrule
\vspace{0.5em}
{\color{tfe-gray}\small This document is confidential and for
internal use only. The ArcLoom SPPU architecture is the
intellectual property of Joseph Forrester / DSF-AI. The
calibration methodology (DSF-AI blade) is a trade secret and is
not disclosed in this document.}

\end{document}
